Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-05-04 automatica/paper.tex
Updated Axelerator results

  There are a number of algorithms in our verification engine that can
  be used for stability analysis~\cite{daes20161, Bessa16}.
%one based on Schur's decomposition
%and another one based on Jury's criterion~\cite{astrom1997computer}.  
Here we choose Jury stability criterion~\cite{astrom1997computer} in view of its efficiency 
and ease of integration within our implementation: 
this method checks the stability working in the $z$-domain of the characteristic polynomial $S(z)$,  
%
% of the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the closed-loop system output and U(z) is the controller output. 
%% \red{[unclear: what matrix? We need to clarify the relationship
%% between the char. poly. $S(z)$ and the later quantities $\Delta
%% N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's
%% structure.]}.
%
considered in its general form as 
% for $S(z)$:
%
\begin{equation*}
S(z) = a_0z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0. 
\end{equation*}
%\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?} 
% Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
% and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
% $$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
The following matrix
$M = [m_{ij}]_{(2N-2)\times N}$ is built from $S(z)$ coefficients:
%
$$
M=\left( 
\begin{array}{c}
V^{(0)}\\
V^{(1)}\\
\vdots\\
V^{(N-2)}
\end{array}
\right), 
$$
%
where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
%
$$
v_{ij}^{(0)}=\left\{
\begin{array}{ll}
a_{j-1}, & \mbox{if}~i=1\\
v_{(1)(N-j+1)}^{0},&\mbox{if}~i=2
\end{array}
\right.
$$
%
$$
v_{ij}^{(k)}=\left\{
\begin{array}{ll}
0,&\mbox{if}~j>n-k\\
v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \mbox{if}~j\leq n-k ~\mbox{and}~i=1\\
v_{(1)(N-j+1)}^{k},& \mbox{if}~j\leq n-k ~\mbox{and}~i=2\\
\end{array}
\right.
$$
%
and where $k \in \mathbb{Z}$ is such that $0 < k < N - 2$. 
We have that $S(z)$ is the characteristic polynomial of a stable system if and only if the following four conditions hold~\cite{astrom1997computer}:
%\begin{itemize}
%\item 
$R_1: S(1) > 0$;
%\item 
$R_2: (−1)^N S(−1) > 0$;
%\item 
$R_3: |a_0| < a_N$;
%\item 
$R_4: m_{11} > 0 \wedge\allowbreak
      m_{31}>0 \wedge\allowbreak
      m_{51}>0 \wedge \ldots \wedge\allowbreak
      m_{(2N{-}3)(1)}>0$.
%\end{itemize}
%
The stability property is then encoded by a constraint of the form:
$
\phi_\mathit{stability} := (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
$

@@

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
1  & Acrobot  & 4 &   &  &  &  & & & &\\
2  & Antenna  & 6 &   &  &  &  & & & &\\
3  & Ballmaglev  & 3 &  &   &  &  & & & &\\
4  & Bioreact & 3 & 16,8 & 11200ms & 16,10 &14600ms & & & &\\
5  & Chen\_ex1& 3 & 16,8 & 7278ms  & 16,10 & 9196ms & & & &\\
6  & Chen\_ex2 & 8& & & 32,23 & 4683872ms &  & & &\\
7  & Chen\_ex3 & 7 &   & & & & & & &\\
8  & Chen\_ex4 & 9 &  & & & & & & &\\
9  & Cruise    & 1 & 16,8 & 6563ms & 16,10 & 6543ms &  & & &\\
10 & CruiseHSCC & 1 & 16,8 & 6587ms & 16,10 & 6567ms &  & & &\\
11 & Cstr & 1 & &  & & & & & &\\
12 & Cstrtmp  & 1 &   &  & & & & & &\\
13 & DCmotor   & 2 & 16,8  & 6879ms & 16,10 & 7786ms & & & &\\
14 & Flexbeam   & 6 &   &  & & & & & &\\
15 & Guidance chen  & 5 &   &  & & & & & &\\
16 & Helicopter   & 3 & 16,8 & 13728ms & 32,23 & 148012ms & & & &\\
17 & Invpendulum\_cartpos & 4 &   &  & & & & & &\\
18 & Invpendulum\_pendang & 2 & 24,12 & 9741ms & 16,10 & 28135ms & & & &\\
19 & Magpointer   & 2 & 16,8 & 10093ms & 16,10 & 20407ms & & & &\\
20 & Magsuspension  & 2 & 12,12  &22146ms  & 16,10 & 34808ms & & & &\\
21 & Pendulum   & 2 & 16,8 & 8503ms & 32,23 & 23987ms & & & &\\
22 & Regulator   & 5 &   &  & & & & & &\\
23 & Springmassdamper & 2 &   &  & & & & & &\\
24 & streamdrum   & 3 & 16,8  & 332422ms & 16,10 & 590501ms & & & &\\
25 & Suspension  & 4 & 16,8  & 17206ms & 16,10 &1372945ms & & & &\\
26 & Tapedriver   & 3 & 16,8  & 8188ms & & & & & &\\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}

>>>>

  There are a number of algorithms in our verification engine that can
  be used for stability analysis~\cite{daes20161, Bessa16}.
%one based on Schur's decomposition
%and another one based on Jury's criterion~\cite{astrom1997computer}.  
Here we choose Jury stability criterion~\cite{astrom1997computer} in view of its efficiency 
and ease of integration within our implementation: 
this method checks the stability working in the $z$-domain of the characteristic polynomial $S(z)$,  
%
% of the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the closed-loop system output and U(z) is the controller output. 
%% \red{[unclear: what matrix? We need to clarify the relationship
%% between the char. poly. $S(z)$ and the later quantities $\Delta
%% N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's
%% structure.]}.
%
considered in its general form as 
% for $S(z)$:
%
\begin{equation*}
S(z) = a_0z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0. 
\end{equation*}
%\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?} 
% Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
% and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
% $$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
The following matrix
$M = [m_{ij}]_{(2N-2)\times N}$ is built from $S(z)$ coefficients:
%
$$
M=\left( 
\begin{array}{c}
V^{(0)}\\
V^{(1)}\\
\vdots\\
V^{(N-2)}
\end{array}
\right), 
$$
%
where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
%
$$
v_{ij}^{(0)}=\left\{
\begin{array}{ll}
a_{j-1}, & \mbox{if}~i=1\\
v_{(1)(N-j+1)}^{0},&\mbox{if}~i=2
\end{array}
\right.
$$
%
$$
v_{ij}^{(k)}=\left\{
\begin{array}{ll}
0,&\mbox{if}~j>n-k\\
v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \mbox{if}~j\leq n-k ~\mbox{and}~i=1\\
v_{(1)(N-j+1)}^{k},& \mbox{if}~j\leq n-k ~\mbox{and}~i=2\\
\end{array}
\right.
$$
%
and where $k \in \mathbb{Z}$ is such that $0 < k < N - 2$. 
We have that $S(z)$ is the characteristic polynomial of a stable system if and only if the following four conditions hold~\cite{astrom1997computer}:
%\begin{itemize}
%\item 
$R_1: S(1) > 0$;
%\item 
$R_2: (-1)^N S(-1) > 0$;
%\item 
$R_3: |a_0| < a_N$;
%\item 
$R_4: m_{11} > 0 \wedge\allowbreak
      m_{31}>0 \wedge\allowbreak
      m_{51}>0 \wedge \ldots \wedge\allowbreak
      m_{(2N{-}3)(1)}>0$.
%\end{itemize}
%
The stability property is then encoded by a constraint of the form:
$
\phi_\mathit{stability} := (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
$

@@

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
1  & Acrobot  & 4 &   &  &  &  & & & &\\
2  & Antenna  & 6 &   &  &  &  & & & &\\
3  & Ballmaglev  & 3 &  &   &  &  & & & &\\
4  & Bioreact & 3 & 16,8 & 11200ms & 16,10 &14600ms & 24,14 & 425ms& 16,10 & 502ms\\
5  & Chen\_ex1& 3 & 16,8 & 7278ms  & 16,10 & 9196ms & & & 16,10 & 1398ms\\
6  & Chen\_ex2 & 8& & & 32,23 & 4683872ms &  & & &\\
7  & Chen\_ex3 & 7 &   & & & & & & &\\
8  & Chen\_ex4 & 9 &  & & & & & & &\\
9  & Cruise    & 1 & 16,8 & 6563ms & 16,10 & 6543ms & 24,14 & 295ms& 16,10 & 306ms\\
10 & CruiseHSCC & 1 & 16,8 & 6587ms & 16,10 & 6567ms &  24,14 &293ms& 16,10 & 313ms\\
11 & Cstr & 1 & &  & & & & & &\\
12 & Cstrtmp  & 1 &   &  & & & 24,14 &478ms& &\\
13 & DCmotor   & 2 & 16,8  & 6879ms & 16,10 & 7786ms & 24,14 & 435ms& 16,10 & 520ms\\
14 & Flexbeam   & 6 &   &  & & & 24,14 &72079ms& &\\
15 & Guidance chen  & 5 &   &  & & & & & &\\
16 & Helicopter   & 3 & 16,8 & 13728ms & 32,23 & 148012ms & 24,14 & 727ms& 16,10 &1075ms\\
17 & Invpendulum\_cartpos & 4 &   &  & & & & & &\\
18 & Invpendulum\_pendang & 2 & 24,12 & 9741ms & 16,10 & 28135ms & 24,14 & 432ms& 16,10 &466ms\\
19 & Magpointer   & 2 & 16,8 & 10093ms & 16,10 & 20407ms & 24,14  & 916ms& 16,10 &1244ms\\
20 & Magsuspension  & 2 & 12,12  &22146ms  & 16,10 & 34808ms & 24,14 & 443ms & 16,10 &569ms\\
21 & Pendulum   & 2 & 16,8 & 8503ms & 32,23 & 23987ms & 24,14 & 395ms& 16,10 &473ms\\
22 & Regulator   & 5 &   &  & & & & & &\\
23 & Springmassdamper & 2 &   &  & & & & & &\\
24 & streamdrum   & 3 & 16,8  & 332422ms & 16,10 & 590501ms & 24,14 & 701ms& 16,10 &1225ms\\
25 & Suspension  & 4 & 16,8  & 17206ms & 16,10 &1372945ms & 56,30 & 15268ms& 16,10 &4374ms\\
26 & Tapedriver   & 3 & 16,8  & 8188ms & & & 64,22 & 2026ms& 16,10 &1090ms\\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}
